---
title: "English Grammar"
author: "Ajay Koli"
subtitle: "Nalanda Academy"
date: "2022-10-12 (updated on `r Sys.Date()`)"
format: revealjs
editor: visual
scrollable: true
execute: 
  echo: false
---

# Simple Present Tense

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = 0, font_size = "2em")
```

1.  वह मोटरसाइकिल चलाता है।

2.  वे मांस नहीं भूनते हैं।

3.  क्या छात्र अपने शिक्षक को नमस्कार करते हैं?

4.  शिक्षक अपने छात्रों की रक्षा नहीं करता है

5.  इस तस्वीर में अभिनेता ने अच्छे कपड़े नहीं पहने हैं।

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = 0, font_size = "2em")
```

1.  मोहन प्रत्येक रविवार को कपड़े साफ करता है।

2.  बंदर पेड़ के पीछे छिप गया।

3.  रानी जवाब भूल जाती है।

4.  ड्राइवर शीशा पोंछता है।

5.  कुत्ता काटता है।

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = 0, font_size = "2em")
```

1.  मच्छर मुझे परेशान करते हैं।

2.  क्या आप अपने बालों को रंगते हैं?

3.  हम रोज टहलने जाते हैं।

4.  क्या वह किराए पर रहता है?

5.  मेरी मां दही में चीनी मिलाती हैं।

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = 0, font_size = "2em")
```

1.  मोबाइल फोन मेरी पढ़ाई में खलल डालता है।

2.  चूहा बिल्ली का पीछा करता है।

3.  मेरे पापा नाश्ते में अंडे उबालते हैं।

4.  क्या वह चिल्लाता है?

5.  वह फुटबॉल खेलती है।

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = 0, font_size = "2em")
```

1.  वह नागालैंड का रहने वाला है।

2.  वे कार्यालय के कर्मचारियों के बारे में गपशप करते हैं।

3.  छात्र शिक्षक पर हंसते हैं।

4.  राजनेता देश के बारे में लिखते हैं।

5.  वह संगीत नहीं सुनती

# Date: TEST 8 Nov 2022

<iframe src="https://giphy.com/embed/l2Sq5hjCE8ZnHGYdG" width="480" height="270" frameBorder="0" class="giphy-embed" allowFullScreen>

</iframe>

<p><a href="https://giphy.com/gifs/southparkgifs-l2Sq5hjCE8ZnHGYdG">via GIPHY</a></p>

## "To Be" Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "6%", font_size = "2em")
```

1.  It ......... true.
2.  They ......... here.
3.  We .......... busy.
4.  I ............. ready.
5.  My aunt ............. nice.
6.  Ravi and Mohan ................. brothers.
7.  The ribbon .......... blue.
8.  You ................ tired.

## "To Be" Present Tense: Negative Form

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "6%", font_size = "2em")
```

1.  The train ............. full today.

2.  The keys ................ in the car.

3.  The eraser ........... in the pencil case.

4.  She ................ a teacher in my school.

5.  The woman .......... old.

6.  The bowls ........... on the table.

7.  The store .............. far.

8.  It ............ true.

## "To Be" Present Tense: Question Form

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "6%", font_size = "2em")
```

1.  ............... it cold in Canada?

2.  ................ they in the living room?

3.  ................ the forks in the dishwasher?

4.  ................ the ink in the printer?

5.  ............... the nail polish purple?

6.  ................. I nice?

7.  .................. they there?

8.  ............ the pearls real?

## "To Be" Past Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "6%", font_size = "2em")
```

1.  He .............. in the shower.

2.  The girls ............ at the skating ring.

3.  The moon .............. bright last night.

4.  My pockets ............. full.

5.  The eggs .............. on the counter.

6.  You ........... at the wedding.

7.  Both pillows ................. soft.

8.  The teachers ........... are in the office.

## Simple Present Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "-6%", font_size = "2em")
```

1.  My teacher ............. (to explain) everything.

2.  Lisa ............. (to buy) a lot of perfume.

3.  The boys ....... (to obey) the rules in class.

4.  The snow ....... (to melt) in the spring.

5.  They ......... (to earn) a lot of money.

6.  I ......... (to work) in the local bank.

7.  You ....... (to owe) me money.

8.  He ....... (to spoil) his child.

## Simple Present Tense

#### Negative Form

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "-6%", font_size = "2em")
```

1.  She ............. write to Ajay.

2.  It ............... hurt.

3.  We ............... feed the stray cats.

4.  You ....... laugh a lot.

5.  It ............. belong to you.

6.  I .......... need a towel.

7.  Iron man .......... want cotton candy.

8.  They ......... walk in the morning.

## Simple Present Tense

#### Question Form

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "-6%", font_size = "2em")
```

1.  .......... Lisa participate at school?

2.  ........... you dog chase cats?

3.  ........... it interest you?

4.  .............. you dye your hair?

5.  .......... they walk to school?

6.  ............. the noise disturb you?

7.  ........... the children like peas?

8.  ............. students hate their English teacher?

## Simple Past Tense

```{r}
library(countdown)
countdown::countdown(minutes = 5, top = "-6%", font_size = "2em")
```

1.  David .......... (to swear) in class today.
2.  We ............ (to hear) your speech last night, and it was great.
3.  We ........ (to see) a mouse in the pantry last night.
4.  I ......... (to begin) my homework after school.
5.  I ....... (to tidy) the house for my mother.
6.  I ......... (to decide) to learn English.
7.  We ........ (to expect) to see you there.
8.  I was alert and I ........ (to avoid) the collision.
